---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# diaper

This is a package to create a `DESCRIPTION` file for your project that lists
specific dependencies and versions of packages needed for analysis. Yes, 
packages like [packrat] exist, but I've found it to be a bit cumbersome. With a
`DESCRIPTION` file, it's possible to list the packages you need for an analysis
and install them with [devtools].

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Travis-CI Build Status](https://travis-ci.org/zkamvar/diaper.svg?branch=master)](https://travis-ci.org/zkamvar/diaper)

## Making Your DESCRIPTION file

Here's an example of creating a DESCRIPTION file using the [RClone] and [dplyr] 
packages.


First, you use `add()` to add dependiencies to your DESCRIPTION file. If
the file doesn't exist, it will simply be created.

```{r}
tmp <- tempdir() # when using this for your own project, simply keep this as
                 # your current directory
diaper::add(c("RClone (>= 1.0.2)", "dplyr (>= 0.5.0)"), 
            field = "Imports", 
            file = file.path(tmp, "DESCRIPTION"), 
            name = "RCanalysis",
            write = TRUE)
# View the file that we just created
write.dcf(read.dcf(file.path(tmp, "DESCRIPTION")))
```

Now with [devtools], we can install the package!

```{r, message = TRUE}
devtools::install(tmp)
```

We can also update fields such as the default version of R. Note that we don't
need the `name` parameter here, because the file already exists.

```{r}
diaper::add("R (>= 3.2.0)",
            field = "Depends",
            file = file.path(tmp, "DESCRIPTION"),
            write = TRUE)
write.dcf(read.dcf(file.path(tmp, "DESCRIPTION")))
```



## Roadmap

This may be the only iteration of the package, but if there is interest, it could
be made more user-friendly with the following:

- Customization of more DESCRIPTION fields (i.e. Authors@R)
- Bioconductor repositories
- Remotes
- SystemRequirements
- RStudio add-in
- Shiny app


[packrat]: https://cran.r-project.org/package=packrat
[devtools]: https://cran.r-project.org/package=devtools
[dplyr]: https://cran.r-project.org/package=dplyr
[RClone]: https://cran.r-project.org/package=RClone
